\textbf{\Large Computer Vision-based System for Impaired Human Vision Compensation}

### 2018-09-30 bare_conf.tex
text changes, Results section is rewritten

More than $250$ million poople worldwide have moderate to severe vision impairment, while ($\approx 36$ million are blind) \cite{Bourne}. During the past decades significant effort was devoted to develop computer vision and other sensor based aids (e.g. \cite{Caraiman}, \cite{Csapo}, \cite{Poggi}, \cite{Zientara}) for helping the blind and visually impaired users to perceive the surrounding world. However, computer vision is rapidly evolving field, and systems based on the aforementioned approaches often lack accuracy and reliability in real-world conditions. In this article we describe a system, which employs modern computer vision techniques for compensation of lost or impaired vision function in humans. Many of the previuosly proposed electronic aids for the blind count on highly specialised hardware, for instance smart glassess \cite{Zientara}, Microsoft Kinnect sensors \cite{Owayjan}, helmet-mounted photosensors and cameras \cite{Larisa}. Such advanced and costly technology brings additional complexity into daily tasks, which visually impaired people currently manage by the help of a white cane. This project puts major emphasis on developing a tool, which seamlesly integrates with the hardware visually impaired person already has on-hand and is used to (smartphone). This paper describes a high level architecture of the proposed technology aid for visually impaired people.

@@

Following the principles of participatory design \cite{Kensing}, \cite{Carroll} we included the final users into the design process of the system. Two visually impaired persons participated in discussion and focus group meetings together with the project team to identify the key properties of the solution. During the six discussion sessions major attention was paid to:
\begin{enumerate}
\item Functionality and key features of the solution addressing real-life scenarios of visually impaired persons;
\item Technical feasibility, connecting user needs to the latest development in computer vision and assisted technologies;
\item Interface between the visually impaired person and the assisted technology;
\item Appearance, usability and potential costs of the final product. 
\end{enumerate}
Design process involved testing of the existing tmobile phone app (Seeing AI) for assisting visually impaired persons. Semi-structured tests were performed by the visually impaired participants accompanied by a researcher from a project group. Strengths and weaknesses of the existing solutions are reflected in the design of the proposed system.

@@

%\begin{wrapfigure}{r}{0.4\textwidth}
\begin{figure}
  \begin{center}
    \includegraphics[scale=0.7]{./img/cropped_diagram.pdf}  
  \end{center}
  \caption{Schematics of FRP device.}
  \label{fig:schematics}
\end{figure}
%\end{wrapfigure}

Following the above methodology we suggest the impaired human vision compensation system (\textbf{HVCS}), consisting of \textbf{Device} and \textbf{Inference} components (see Fig.~\ref{fig:schematics}).

%padalijimas i 2 komponentus man nelabai aiskus. As dalinciau i input (kameros, sensoriai), output (ausines, vibratoriu matricos), processing (local, remote). 
% tai kas dabar yra prie Inference, siulau perfrazuot kaip Functionality, ka as minejau Method. Taip pat visa Results skyreli reiktu labiau susiet su Method. Reiktu, kad visi 4 Method pamineti punktai isrysketu ir Results. 
%Results skyrelyje nereiktu taip stipriai fokusuotis i kitu grupiu tyrimus ir juos cituoti. Rezultatai juk musu.
\textbf{Device} subsystem is a computational device the user currently uses for completing other daily tasks. It consists of sensors and actuators, integrated into smartphone-based computational core, which was chosen due its avialability to wide population, and capability to perform the required computations or forward visual information to the external server via the Internet connection. Sensors are mounted on forehead belt include: RGB camera, depth camera, IMU. Actuator set consists of bone conductive headphones, and head belt for presenting tactile-feedback to the user. %We suggest to use bone conductive headphones, ...

\textbf{Inference} subsystem consists of server computer with internet connection and set of computer vision algorithms, selected according to our methodology (see. Sec.~\ref{sec:method}): Faster RCNN object detector \cite{?}, trained to detect important objects (doors, floors, elevators, stairs, corridor junctions, etc.), CNN-RNN-based scene description \cite{Liu},\cite{Ren}, \cite{Dai}, place recognition \cite{Ohn-Bar}, face recognition \cite{Amos}, obstacle detection \cite{Laina}, and possibly other modules.

HVCS operation cycle is started by \textbf{Device} reading sensor data and transmitting it to the server for an analysis. Server calculates feedback signal and transmits it back to the device for presenting to the user.

@@

>>>>

More than $250$ million people worldwide have moderate to severe vision impairment, while ($\approx 36$ million are blind) \cite{Bourne}. During the past decades significant effort was devoted to develop computer vision and other sensor based aids (e.g. \cite{Caraiman}, \cite{Csapo}, \cite{Poggi}, \cite{Zientara}) for helping the blind and visually impaired users to perceive the surrounding world. However, computer vision is rapidly evolving field, and systems based on the aforementioned approaches often lack accuracy and reliability in real-world conditions. In this article we describe a system, which employs modern computer vision techniques for compensation of lost or impaired vision function in humans. Many of the previously proposed electronic aids for the blind count on highly specialized hardware, for instance smart glasses \cite{Zientara}, Microsoft Kinnect sensors \cite{Owayjan}, helmet-mounted photo sensors and cameras \cite{Larisa}. Such advanced and costly technology brings additional complexity into daily tasks, which visually impaired people currently manage by the help of a white cane. This project puts major emphasis on developing a tool, which seamlessly integrates with the hardware visually impaired person already has on-hand and is used to (smartphone). This paper describes a high level architecture of the proposed technology aid for visually impaired people.

@@

Following the principles of participatory design \cite{Kensing}, \cite{Carroll} we included the final users into the design process of the system. Two visually impaired persons participated in discussion and focus group meetings together with the project team to identify the key properties of the solution. During the six discussion sessions major attention was paid to:
\begin{enumerate}
\item Functionality and key features of the solution addressing real-life scenarios of visually impaired persons;
\item Technical feasibility, connecting user needs to the latest development in computer vision and assisted technologies;
\item Interface between the visually impaired person and the assisted technology;
\item Appearance, usability and potential costs of the final product. 
\end{enumerate}
Design process involved testing of the existing mobile phone app (Seeing AI) for assisting visually impaired persons. Semi-structured tests were performed by the visually impaired participants accompanied by a researcher from a project group. Strengths and weaknesses of the existing solutions are reflected in the design of the proposed system.

@@

User-centered design sessions with visually impaired persons provided substantial input for the design of the proposed system (Fig.~\ref{fig:schematics}). The process made it clear that understanding of the user needs was limited in the project group. Based on the results of the user-centered design process, we present the outline of the system for impaired human vision compensation.

The key part of the proposed system is a smartphone device, connecting user interface and data processing components into a well-functioning ecosystem. Smartphone was selected due to its high availability and capability to perform required computations or forward visual information to the external server via the Internet connection. The cornerstone of the proposed solution is a wearable forehead belt, integrating two cameras and a tactile feedback device. Bone conductive headphones are suggested to facilitate audio feedback.

%\begin{wrapfigure}{r}{0.4\textwidth}
\begin{figure}
  \begin{center}
    \includegraphics[scale=0.7]{./img/cropped_diagram.pdf}  
  \end{center}
  \caption{Schematics of FRP device.}
  \label{fig:schematics}
\end{figure}

%\end{wrapfigure}

%Following the above methodology we suggest the impaired human vision compensation system (\textbf{HVCS}), consisting of \textbf{Device} and \textbf{Inference} components (see Fig.~\ref{fig:schematics}).

%padalijimas i 2 komponentus man nelabai aiskus. As dalinciau i input (kameros, sensoriai), output (ausines, vibratoriu matricos), processing (local, remote). 
% tai kas dabar yra prie Inference, siulau perfrazuot kaip Functionality, ka as minejau Method. Taip pat visa Results skyreli reiktu labiau susiet su Method. Reiktu, kad visi 4 Method pamineti punktai isrysketu ir Results. 
%Results skyrelyje nereiktu taip stipriai fokusuotis i kitu grupiu tyrimus ir juos cituoti. Rezultatai juk musu.

Discussions on functionality and key features of the solution revealed a gap between the aims of the existing tools, which are often focused on advanced navigation and scene description features, and actual user needs. The end users highlighted that a simplistic solution for navigating is lacking. They were not excited about advanced object detection and scene description techniques, which may overcomplicate their daily life. Major focus was put on a easy to use and minimalistic tool, which can be trusted. Direction and approximate distance to obstacle were highlighted as major requirements. To our surprise, only 5-8 distinctive object classes (for instance, buss stop, pedestrian crossing, doors, stairs, etc) were of major importance while navigating. Additional information, such as type of a passing car, blossoming flowers in the park or person passing riding a bicycle was considered as overwhelming and distractive.

Social networking functionality was accepted as a potentially important feature allowing other users/volunteers to describe certain objects (for instance, temporary road works) with exact location and description. Navigating around such obstacles can be challenging for computer vision-based tools and may decrease user's trust in the tool. Integration of additional information from other users, governmental organizations and volunteers could be of high value for the visually impaired people.

%Povilai, paziurek ar cia viskas OK, pridek ka nors nuo saves
Computer vision technology is under rapid development and during last years made major breakthrough in performance and efficiency. Deep learning neural networks, which are de facto standard in modern image/video processing, are now well supported by software libraries and dedicated hardware built-in even in relatively low-power computational devices, such as smartphones. These devices are equipped with high-quality cameras, 4G Internet connectivity and sufficient computational power to perform initial data processing locally. The maturity of the aforementioned technologies suggest that our proposed computational aid for visually impaired persons may be highly feasible.

The cornerstone of this project is the interface between the visually impaired person and the assistive technology. We are proposing a combination of audio and tactile feedback, which may improve the interaction between the assitive technology and the user. Similar interfaces were suggested by research communities earlier \cite{Zientara}, \cite{Poggi}, however, current knowledge on user preferences and evaluation of various options of tactile feedback (placement on the body, frequencies, strength, etc.) is limited.

Appearance, usability and cost of the final solution is of major importance to the users. The proposed assistive technology should replace/supplement the tool that visually impaired persons used for decades - the white cane. Using a white cane requires little to none training, has very low costs and is relatively reliable. It provides information on the surrounding objects 1-2 meters in front of the user. While the cane can used to detect a nearby obstacle, electronic travel aid could be beneficial for longer range (10-20m) route planning and object recognition. However, it should integrate seamlessly into the existing navigation practices of visually impaired people.

%The proposed system  consists of three major parts: is a computational device the user currently uses for completing other daily tasks. It consists of sensors and actuators, integrated into smartphone-based computational core, which was chosen due its avialability to wide population, and capability to perform the required computations or forward visual information to the external server via the Internet connection. Sensors are mounted on forehead belt include: RGB camera, depth camera, IMU. Actuator set consists of bone conductive headphones, and head belt for presenting tactile-feedback to the user. %We suggest to use bone conductive headphones, ...

%\textbf{Inference} subsystem consists of server computer with internet connection and set of computer vision algorithms, selected according to our methodology (see. Sec.~\ref{sec:method}): Faster RCNN object detector \cite{?}, trained to detect important objects (doors, floors, elevators, stairs, corridor junctions, etc.), CNN-RNN-based scene description \cite{Liu},\cite{Ren}, \cite{Dai}, place recognition \cite{Ohn-Bar}, face recognition \cite{Amos}, obstacle detection \cite{Laina}, and possibly other modules.

%HVCS operation cycle is started by \textbf{Device} reading sensor data and transmitting it to the server for an analysis. Server calculates feedback signal and transmits it back to the device for presenting to the user.

@@

\bibitem{Poggi} Poggi, M., Mattoccia, S. A wearable mobility aid for the visually impaired based on embedded 3D vision and deep learning. 2016 IEEE Symposium on Computers and Communication (ISCC), 2016
